GEEPERs: Principal Stratification using Principal Scores and Stacked Estimating Equations

### 2022-12-19 writeUps/paper.tex

>>>>

\clearpage
\section{Simulation Results}

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.8\textwidth]{simFigs/alphaAUC.pdf}
    \caption{Estimated AUC values from principal score models for each value of $\alpha$ in the simulation, with $n=500$.}
    \label{fig:alphaAUC}
\end{figure}

%\begin{table}
%\caption{Coverage of nominal 95\% confidence intervals}

\begin{tabular}[t]{lllrrlrrlllrrlrr}
\toprule
\multicolumn{3}{c}{ } & \multicolumn{3}{c}{$\alpha=0$} & \multicolumn{3}{c}{$\alpha=0.2$} & \multicolumn{3}{c}{$\alpha=0.5$} \\
\cmidrule(l{3pt}r{3pt}){4-6} \cmidrule(l{3pt}r{3pt}){7-9} \cmidrule(l{3pt}r{3pt}){10-12}
\makecell[l]{Residual\\Dist.} & \makecell[c]{X:Z\\Int.?} & \makecell[r]{X:S\\Int.?} & n & $\beta_1$ & Prin. Eff & GEEPERs & Mix. & \makecell[r]{Residual\\Dist.} & \makecell[l]{X:Z\\Int.?} & \makecell[c]{X:S\\Int.?} & n & $\beta_1$ & Prin. Eff & GEEPERs & Mix.\\
\midrule
 & No & No & 500 & 0.3 & $\tau^0$ & 0.97 & 0.98 & Normal & No & No & 500 & 0.3 & $\tau^0$ & 0.95 & 0.96\\

 & No & No & 500 & 0.3 & $\tau^1$ & 0.97 & 0.97 & Normal & No & No & 500 & 0.3 & $\tau^1$ & 0.96 & 0.96\\

 & Yes & No & 500 & 0.3 & $\tau^0$ & 0.88 & 0.76 & Normal & Yes & No & 500 & 0.3 & $\tau^0$ & 0.94 & 0.89\\

 & Yes & No & 500 & 0.3 & $\tau^1$ & 0.88 & 0.74 & Normal & Yes & No & 500 & 0.3 & $\tau^1$ & 0.94 & 0.89\\

 & No & Yes & 500 & 0.3 & $\tau^0$ & 0.97 & 0.96 & Normal & No & Yes & 500 & 0.3 & $\tau^0$ & 0.96 & 0.97\\

 & No & Yes & 500 & 0.3 & $\tau^1$ & 0.98 & 0.97 & Normal & No & Yes & 500 & 0.3 & $\tau^1$ & 0.97 & 0.96\\

 & Yes & Yes & 500 & 0.3 & $\tau^0$ & 0.90 & 0.76 & Normal & Yes & Yes & 500 & 0.3 & $\tau^0$ & 0.93 & 0.89\\

\multirow{-8}{*}{\raggedright\arraybackslash Normal} & Yes & Yes & 500 & 0.3 & $\tau^1$ & 0.90 & 0.77 & Normal & Yes & Yes & 500 & 0.3 & $\tau^1$ & 0.94 & 0.88\\
\cmidrule{1-16}
 & No & No & 500 & 0.3 & $\tau^0$ & 0.98 & 0.39 & Uniform & No & No & 500 & 0.3 & $\tau^0$ & 0.95 & 0.61\\

 & No & No & 500 & 0.3 & $\tau^1$ & 0.97 & 0.40 & Uniform & No & No & 500 & 0.3 & $\tau^1$ & 0.95 & 0.61\\

 & Yes & No & 500 & 0.3 & $\tau^0$ & 0.87 & 0.21 & Uniform & Yes & No & 500 & 0.3 & $\tau^0$ & 0.94 & 0.48\\

 & Yes & No & 500 & 0.3 & $\tau^1$ & 0.87 & 0.20 & Uniform & Yes & No & 500 & 0.3 & $\tau^1$ & 0.93 & 0.48\\

 & No & Yes & 500 & 0.3 & $\tau^0$ & 0.97 & 0.49 & Uniform & No & Yes & 500 & 0.3 & $\tau^0$ & 0.95 & 0.60\\

 & No & Yes & 500 & 0.3 & $\tau^1$ & 0.98 & 0.53 & Uniform & No & Yes & 500 & 0.3 & $\tau^1$ & 0.96 & 0.57\\

 & Yes & Yes & 500 & 0.3 & $\tau^0$ & 0.89 & 0.21 & Uniform & Yes & Yes & 500 & 0.3 & $\tau^0$ & 0.95 & 0.52\\

\multirow{-8}{*}{\raggedright\arraybackslash Uniform} & Yes & Yes & 500 & 0.3 & $\tau^1$ & 0.88 & 0.21 & Uniform & Yes & Yes & 500 & 0.3 & $\tau^1$ & 0.94 & 0.53\\
\cmidrule{1-16}
 & No & No & 1000 & 0.3 & $\tau^0$ & 0.96 & 0.97 & Normal & No & No & 1000 & 0.3 & $\tau^0$ & 0.94 & 0.94\\

 & No & No & 1000 & 0.3 & $\tau^1$ & 0.97 & 0.97 & Normal & No & No & 1000 & 0.3 & $\tau^1$ & 0.95 & 0.96\\

 & Yes & No & 1000 & 0.3 & $\tau^0$ & 0.89 & 0.60 & Normal & Yes & No & 1000 & 0.3 & $\tau^0$ & 0.94 & 0.80\\

 & Yes & No & 1000 & 0.3 & $\tau^1$ & 0.90 & 0.60 & Normal & Yes & No & 1000 & 0.3 & $\tau^1$ & 0.93 & 0.79\\

 & No & Yes & 1000 & 0.3 & $\tau^0$ & 0.97 & 0.96 & Normal & No & Yes & 1000 & 0.3 & $\tau^0$ & 0.95 & 0.97\\

 & No & Yes & 1000 & 0.3 & $\tau^1$ & 0.97 & 0.97 & Normal & No & Yes & 1000 & 0.3 & $\tau^1$ & 0.94 & 0.96\\

 & Yes & Yes & 1000 & 0.3 & $\tau^0$ & 0.91 & 0.62 & Normal & Yes & Yes & 1000 & 0.3 & $\tau^0$ & 0.95 & 0.83\\

\multirow{-8}{*}{\raggedright\arraybackslash Normal} & Yes & Yes & 1000 & 0.3 & $\tau^1$ & 0.91 & 0.62 & Normal & Yes & Yes & 1000 & 0.3 & $\tau^1$ & 0.91 & 0.81\\
\cmidrule{1-16}
 & No & No & 1000 & 0.3 & $\tau^0$ & 0.95 & 0.01 & Uniform & No & No & 1000 & 0.3 & $\tau^0$ & 0.96 & 0.31\\

 & No & No & 1000 & 0.3 & $\tau^1$ & 0.95 & 0.01 & Uniform & No & No & 1000 & 0.3 & $\tau^1$ & 0.96 & 0.30\\

 & Yes & No & 1000 & 0.3 & $\tau^0$ & 0.91 & 0.00 & Uniform & Yes & No & 1000 & 0.3 & $\tau^0$ & 0.91 & 0.17\\

 & Yes & No & 1000 & 0.3 & $\tau^1$ & 0.90 & 0.00 & Uniform & Yes & No & 1000 & 0.3 & $\tau^1$ & 0.92 & 0.17\\

 & No & Yes & 1000 & 0.3 & $\tau^0$ & 0.96 & 0.07 & Uniform & No & Yes & 1000 & 0.3 & $\tau^0$ & 0.97 & 0.41\\

 & No & Yes & 1000 & 0.3 & $\tau^1$ & 0.95 & 0.07 & Uniform & No & Yes & 1000 & 0.3 & $\tau^1$ & 0.97 & 0.40\\

 & Yes & Yes & 1000 & 0.3 & $\tau^0$ & 0.89 & 0.03 & Uniform & Yes & Yes & 1000 & 0.3 & $\tau^0$ & 0.95 & 0.22\\

\multirow{-8}{*}{\raggedright\arraybackslash Uniform} & Yes & Yes & 1000 & 0.3 & $\tau^1$ & 0.87 & 0.03 & Uniform & Yes & Yes & 1000 & 0.3 & $\tau^1$ & 0.92 & 0.21\\
\bottomrule
\end{tabular}

%\end{table}
